Extending Morphological Chains with Supervised Learning and Cross-Language Features

### 2015-12-10 paper/paper.tex
paper stuf

Note that parent words usually undergo changes only when attaching suffixes. Thus there is one \emph{Prefix} class, but there are a variety of suffix classes. When acquiring a suffix, the parent word can: (1) undergo no change (\emph{class} $\rightarrow$ \emph{classes}), (2) repeat a character (\emph{star} $\rightarrow$ \emph{starring}), (3) delete a character (\emph{believe} $\rightarrow$ \emph{believing}), (4) modify a character (\emph{parry} $\rightarrow$ \emph{parried}). These correspond to the candidates (\emph{class}, \emph{Suffix}), (\emph{star}, \emph{Repeat}), (\emph{believe}, \emph{Delete}), and (\emph{parry}, \emph{Modify}). Finally, there is a \emph{Stop} type, which is used to signify that the word is a base word.

@@

In our work, we generate 200-dimensional vectors for words by using Word2Vec, which looks at word alignment  and co-occurrence patterns across many documents. In generating our vectors, we use text from Wikipedia along with a corpus of news articles.

@@

\section{Experimental Validation}

\subsection{Data}

We used the datasets provided by 2010 Morpho Challenges. For English, this includes
a wordlist with word frequencies of approximately 878,000 words scraped from the
Wortschatz collection from the University of Leipzig, CLEF, and the Europarl corpus
as well as gold standard segmentation training and development sets of approximately 
1000 randomly selected words. Gold standard segmentation is based on the CELEX database.
For Turkish, the word list contains approximately

\begin{center}
    \begin{tabular}{ | l | l | l | l | l |}
    \hline
    Language & Method & Precision & Recall & F1 \\ \hline
      & Narasimhan & 0.807 & 0.722 & 0.762 \\ 
    & Unsupervised & -  & - & - \\ 
    English & Semi-supervised & - & - & - \\ 
     & Two language unsupervised & - & - & - \\ 
     & Two language semi-supervised & - & - & - \\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 \\ 
    & Unsupervised & - & - & - \\ 
    Turkish & Semi-supervised & - & - & -  \\ 
     & Two language unsupervised  & - & - & -  \\ 
     & Two language semi-supervised  & - & - & -  \\ \hline
    \end{tabular}
\end{center}

\begin{center}
    \begin{tabular}{ | l | l | l | l | l | l |}
    \hline
    Language & \multicolumn{2}{|c|}{\textbf{Correct Segmentations}} & \multicolumn{3}{|c|}{\textbf{Incorrect Segmentations}}\\ \hline
      & Narasimhan & 0.807 & 0.722 & 0.762& - \\ 
    & Unsupervised & -  & - & - & -\\ 
    English & Semi-supervised & - & - & - & -\\ 
     & Two language unsupervised & - & - & -& - \\ 
     & Two language semi-supervised & - & - & - & -\\ \hline
     & Narasimhan & 0.743 & 0.520 & 0.612 & -\\ 
    & Unsupervised & - & - & - & -\\ 
    Turkish & Semi-supervised & - & - & -  & -\\ 
     & Two language unsupervised  & - & - & -  & -\\ 
     & Two language semi-supervised  & - & - & -  & -\\ \hline
    \end{tabular}
\end{center}

>>>>

Note that parent words usually undergo changes only when attaching suffixes. Thus there is one \emph{Prefix} class, but there are a variety of suffix classes. When acquiring a suffix, the parent word can:
\begin{enumerate}
    \item undergo no change (\emph{class} $\rightarrow$ \emph{classes})
    \item repeat a character (\emph{star} $\rightarrow$ \emph{starring})
    \item delete a character (\emph{believe} $\rightarrow$ \emph{believing})
    \item modify a character (\emph{parry} $\rightarrow$ \emph{parried}).
\end{enumerate}
These correspond to the candidates (\emph{class}, \emph{Suffix}), (\emph{star}, \emph{Repeat}), (\emph{believe}, \emph{Delete}), and (\emph{parry}, \emph{Modify}). Finally, there is a \emph{Stop} type, which is used to signify that the word is a base word.

@@

In our work, we generate 200-dimensional vectors for words by using Word2Vec, which looks at word alignment  and co-occurrence patterns across many documents. In generating our vectors, we use text from Wikipedia,
to generate the english word vectors, along with the BOUN corpus of news articles to generate Turkish word vectors.

@@
